Using Distributed Information Stores for Patient-Clinician Health Data Sharing

### 2013-01-15 patient-clinician-workshop/pccworkshop.tex
phrs

In this position paper, we look at the potential and problems of
augmenting the next generation of EHRs with \emph{personal activity
  diaries}, portraits of a person's dynamic condition captured at high
temporal fidelity.  Such activity diaries, we posit, could be derived
from a combination of automatically-sensed activity and vital
statistics through a wide array of available consumer-grade
network-enabled activity senors and diagnostic tools, as well as
through manual annotations provided by patients about their day.

\section{Personal Electronic Sensors}

There has been a surge in popularity of personal electronic sensors as
part of the ``quantified-self'' movement to measure and improve one's health.
Wireless sensors such as the Fit-bit and Nike FuelBand and small and discreet,
yet provide the wearer with a wealth of information about their own activity level.
In particular, wearers have a desire to improve their health and fitness, based on
the feedback they receive from their device.

>>>>

In this position paper, we look at the potential and problems of
augmenting the next generation of EHRs with \emph{personal activity
  diaries}, portraits of a person's dynamic condition captured at high
temporal fidelity.  Such activity diaries are intended to supplement,
rather than supplant, the existing diagnostic reports performed by
professionals, first and foremost, to help clinicians derive a more
complete picture of the person throughout a period of care, such as an
intervention.  We believe that such activity diaries could potentially
also be beneficial to individuals as well, making people more aware of
the evolution of their health.

Nonetheless, challenges abound. These primarily pertain to capturing
these activity diaries, effectively storing these diaries, and privacy
controls for giving patients the ability to disclose desired quantities
of their diary to their clinicians.  We discuss these, next.

\section{Capturing activity diaries}
There has been a surge in popularity of personal electronic sensors as
part of the ``quantified-self'' movement to measure and improve one's health.
Wireless sensors such as the Fit-bit and Nike FuelBand and small and discreet,
yet provide the wearer with a wealth of information about their own activity level.
In particular, wearers have a desire to improve their health and fitness, based on
the feedback they receive from their device.
